Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-05-03 concurrency/CONCUR 2023/paper.tex
small font tweaks

\begin{figure}[h]
	\centering
	\begin{mathpar}
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\texttt{pn->n->t}\mapsto (k', v', l, r)
			\end{array}
			\right\}
		}
		\\ 
		\texttt{findNext(pn, k)} 
		\\
		{\color{blue}
			\left\{\mathit{res}. \ \exists \  n'.
			\begin{array}{c}
				\texttt{pn->n->t}\mapsto (k', v', l, r)  \\\  
				\ast \ (\mathsf{if}\ \mathit{res}\ \mathsf{then}\ (l = n' \land \texttt{k} < k') \lor (r = n' \land \texttt{k} > k')\ \mathsf{else}\ (n = n' \land \texttt{k} = k'))
			\end{array}
			\right\}
		}
	\end{mathpar}
	\caption{Specification of \texttt{findNext} for the binary search tree (all templates)}
	\label{fig:findNext_lock}
\end{figure}

\begin{figure}[h]
	\begin{subfigure}{\textwidth}
	\centering
	\begin{mathpar}
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\ \texttt{pn->n} \mapsto \texttt{NULL}  
			\end{array}
			\right\}
		}
		\\ 
		\texttt{insertOp(pn, k, v)} 
		\\
		{\color{blue}
			\left\{\exists \  l\ r\ \mathit{lk}_1\ \mathit{lk}_2.
			\begin{array}{l}
				\ \texttt{pn->n->t} \mapsto (\texttt{k}, \texttt{v}, l, r) \ \ast \ \\ 
				\ l \mapsto (\texttt{NULL}, \mathit{lk}_1)\  \ast \ r \mapsto (\texttt{NULL}, \mathit{lk}_2)
			\end{array}
			\right\}
		}
		\end{mathpar}
		\caption{Specification of \texttt{insertOp} for the lock-coupling template}
			\label{fig:insertOp_lock}
	\end{subfigure}
	%insertOp for give-up of give-up
	\begin{subfigure}{\textwidth}
		\begin{mathpar}
	{\color{blue}
		\left\{ 
		\begin{array}{c}
			\texttt{pn->n}\mapsto \texttt{NULL} \  \ast \ \texttt{pn->n->min}\mapsto \mathsf{n_1} \ \ast \ \texttt{pn->n->max}\mapsto\mathsf{n_2}
		\end{array}
		\right\}
	}
	\\
	\texttt{insertOp(pn, k, v)}
	\\
	{\color{blue}
		\left\{\exists \ l\ r\ \mathit{lk}_1\ \mathit{lk}_2. 
		\begin{array}{c}
			\texttt{pn->n->t}\mapsto (\texttt{k}, \texttt{v}, l, r) \  \ast \ \texttt{pn->n->min}\mapsto \mathsf{n_1} \ \ast \ \texttt{pn->n->max}\mapsto\mathsf{n_2}  \ \ast \ 
			\\ l \mapsto (\texttt{NULL}, \mathit{lk}_1, (\mathsf{n_1}, \texttt{k})) \ \ast \ r \mapsto (\texttt{NULL}, \mathit{lk}_2, (\texttt{k}, \mathsf{n_2}))
		\end{array}
		\right\}
	}
	\end{mathpar}
	\caption{Specification of \texttt{insertOp} for the give-up template}
	\label{fig:insertOp_giveup}
\end{subfigure}
	\caption{Specification of \texttt{insertOp} for the lock-coupling and give-up templates}
	\label{fig:insertOp}
\end{figure}

@@

\begin{figure}[!ht]
	$\color{blue}
	\forall \  m. \left\langle
	\begin{array}{c}
		\texttt{pn} \mapsto (\texttt{p, n}) \ \ast \ \nodeboxrep(\texttt{n}) \ \big| \ \treerep\ m
	\end{array}
	\right\rangle$
		\lstinputlisting[language=C, style=myStyle, mathescape=true]{proof_giveup_traverse.c}
	$\color{blue}
	\left\langle \mathit{res}. \ \exists \  \texttt{n'}.
	\begin{array}{l} \texttt{pn} \mapsto (\texttt{n', n'}) \ \ast \nodeboxrep(\texttt{n'}) \ \ast \ \texttt{k} \in \mathsf{range}\ \ast \ 
		\\ 
		\mathsf{if} \ \mathit{res} \ \mathsf{then} \ \mathsf{node\_contents}(\texttt{n'}, \cdot, \mathsf{range}) \ 
		\\ \ \ \ \ \ \ \ \ \ \mathsf{else} \ \mathsf{node\_contents}(\texttt{n'}, (\mathsf{k}, v), \mathsf{range})
	\end{array}
	\ \Bigg| \ \treerep\ m \
	\right\rangle$
	\caption{Proof outline of the give-up \texttt{traverse} function}
	\label{proof_giveup_traverse}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{mathpar}
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\texttt{pn->n->t}\mapsto (k', v', l, r)
			\end{array}
			\right\}
		}
		\\ 
		\texttt{findNext(pn, k)} 
		\\
		{\color{blue}
			\left\{\mathit{res}. \ \exists \  n'.
			\begin{array}{c}
				\texttt{pn->n->t}\mapsto (k', v', l, r)  \ \ast \\\  
				(\mathsf{if}\ \mathit{res}\ \mathsf{then}\ (l = n' \land \texttt{k} < k') \lor (r = n' \land \texttt{k} > k')\ \mathsf{else}\ (n = n' \land \texttt{k} = k'))
			\end{array}
			\right\}
		}
	\end{mathpar}
	\caption{Specification of \texttt{findNext} for the binary search tree (all templates)}
	\label{fig:findNext_lock}
\end{figure}

\begin{figure}[h]
	\begin{subfigure}{\textwidth}
	\centering
	\begin{mathpar}
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\ \texttt{pn->n} \mapsto \texttt{NULL}  
			\end{array}
			\right\}
		}
		\\ 
		\texttt{insertOp(pn, k, v)} 
		\\
		{\color{blue}
			\left\{\exists \  l\ r\ \mathit{lk}_1\ \mathit{lk}_2.
			\begin{array}{l}
				\ \texttt{pn->n->t} \mapsto (\texttt{k}, \texttt{v}, l, r) \ \ast \ \\ 
				\ l \mapsto (\texttt{NULL}, \mathit{lk}_1)\  \ast \ r \mapsto (\texttt{NULL}, \mathit{lk}_2)
			\end{array}
			\right\}
		}
		\end{mathpar}
		\caption{Specification of \texttt{insertOp} for the lock-coupling template}
			\label{fig:insertOp_lock}
	\end{subfigure}
	%insertOp for give-up of give-up
	\begin{subfigure}{\textwidth}
		\begin{mathpar}
	{\color{blue}
		\left\{ 
		\begin{array}{c}
			\texttt{pn->n}\mapsto \texttt{NULL} \  \ast \ \texttt{pn->n->min}\mapsto n_1 \ \ast \ \texttt{pn->n->max}\mapsto n_2
		\end{array}
		\right\}
	}
	\\
	\texttt{insertOp(pn, k, v)}
	\\
	{\color{blue}
		\left\{\exists \ l\ r\ \mathit{lk}_1\ \mathit{lk}_2. 
		\begin{array}{c}
			\texttt{pn->n->t}\mapsto (\texttt{k}, \texttt{v}, l, r) \  \ast \ \texttt{pn->n->min}\mapsto n_1 \ \ast \ \texttt{pn->n->max}\mapsto n_2  \ \ast \ 
			\\ l \mapsto (\texttt{NULL}, \mathit{lk}_1, (n_1, \texttt{k})) \ \ast \ r \mapsto (\texttt{NULL}, \mathit{lk}_2, (\texttt{k}, n_2))
		\end{array}
		\right\}
	}
	\end{mathpar}
	\caption{Specification of \texttt{insertOp} for the give-up template}
	\label{fig:insertOp_giveup}
\end{subfigure}
	\caption{Specification of \texttt{insertOp} for the lock-coupling and give-up templates}
	\label{fig:insertOp}
\end{figure}

@@

\begin{figure}[!ht]
	$\color{blue}
	\forall \  m. \left\langle
	\begin{array}{c}
		\texttt{pn} \mapsto (p, n) \ \ast \ \nodeboxrep(n) \ \big| \ \treerep\ m
	\end{array}
	\right\rangle$
		\lstinputlisting[language=C, style=myStyle, mathescape=true]{proof_giveup_traverse.c}
	$\color{blue}
	\left\langle \mathit{res}. \ \exists \  n'.
	\begin{array}{l} \texttt{pn} \mapsto (n', n') \ \ast \nodeboxrep(n') \ \ast \ \texttt{k} \in \mathsf{range}\ \ast \ 
		\\ 
		\mathsf{if} \ \mathit{res} \ \mathsf{then} \ \mathsf{node\_contents}(n', \cdot, \mathsf{range}) \ 
		\\ \ \ \ \ \ \ \ \ \ \mathsf{else} \ \mathsf{node\_contents}(n', (\texttt{k}, \mathsf{v}), \mathsf{range})
	\end{array}
	\ \Bigg| \ \treerep\ m \
	\right\rangle$
	\caption{Proof outline of the give-up \texttt{traverse} function}
	\label{proof_giveup_traverse}
\end{figure}
